The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

  The bipolar jets are constantly ejected from a cylindrical source at the beginning of simulation ($t=0$)\
  and suddenly quenched at $t=1.2$ Myr before fully breaking out the disc.\
  Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
  The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg between\
  $8\times10^{55}$ and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

  The diameter and height of cylindrical source are 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
  much smaller than that of an individual clump by a factor of about 83.\
  By intentionally reducing the volume ratio of the jet source to an individual clump,\
  we can mitigate the effect of the randomness of the clumps on the bubbles.\
  Moreover, we resolve the jet source with the highest refinement level 11,\
  bringing the finest spatial resolution up to 0.4 pc.\

>>>>

  The bipolar jets are constantly ejected from a cylindrical source at the beginning of simulation ($t=0$)\
  and suddenly quenched at $t=1.2$ Myr before fully breaking out the disc.\
  Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
  The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg between\
  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

  The diameter and height of cylindrical source are 4 pc,\
  leading to the source volume ($\sim 50 \text{ pc}^{3}$) is\
  much smaller than that of an individual clump by a factor of about 83.\
  By intentionally reducing the volume ratio of the jet source to an individual clump,\
  we can mitigate the effect of the randomness of the clumps on the bubbles.\
  Moreover, we resolve the jet source with the highest refinement level 11,\
  bringing the finest spatial resolution up to 0.4 pc.\
